---
title       : Height Data Product
subtitle    : Final assignment for Data Products Class
author      : Jay Zuniga
job         : DP Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Height Predictor

This data product allows you to predict your height using
the height of your parents and your gender using the following formula.

$$\frac{dadheight + momheight \pm 5}{2}$$

--- .class #id 

## Using the Galton data set

A good way to check if the model is useful is to use the Galton data set. This data set has 928 observations that on two variables:

1. Mid parent height in inches
2. Chiled height in inches

We'll use the data set to produce a plot using the following R code:

```{r, echo=TRUE, results='hide', fig.show='hide'}
library(HistData)
plot(Galton$parent, Galton$child, xlab="Parents height", ylab="Child height", bg="lightgreen")
fit <- lm(Galton$child ~ Galton$parent)
abline(fit, lwd = 2	)
```

--- .class #id 

## Galton data set

This can be shown in the following plot which charts parent's height vs children's height using the Galton data set.

```{r, echo=FALSE}
library(HistData)
plot(Galton$parent, Galton$child, xlab="Parents height", ylab="Child height", bg="lightgreen")
fit <- lm(Galton$child ~ Galton$parent)
abline(fit, lwd = 2	)
```

--- .class #id 

## Genetic Proof

The Galton data set shows that using the parent's height is a good predictor of a person's future height.

Use the height predictor product now!

--- .class #id 
